---
title: "Appex 07"
author: "Put your name here!"
format: 
  html:
    self-contained: true
editor: visual
---

```{r}
#| label: load-packages
#| message: false
#| warning: false
library(tidyverse)
```

```{r}
#| label: load-data

load("data.rds")

```

Change the `id` below to *your* id. To look up what your ID is go here and enter your email address: https://lucy.shinyapps.io/sta-112-f23-id-lookup/

```{r}
#| label: filter-data

data_sample <- data |>
  filter(id == 9) ## change this to your ID 

```

-   Fit an intercept only model to calculate the average screen time in your sample

```{r}
#| label: model

lm(--- ~ ----, data = data_sample)

```

-   Use the `summary` function on the linear model you fit

```{r}

```

-   What is the standard error for the mean? Interpret this value.

## Part 2

-    Calculate the $t^*$ value for your confidence interval

-   Calculate the confidence interval "by hand" using the $t^*$ value from the previous exercise and the mean and standard error from the previous application exercise

-   Calculate the confidence interval using the \`confint\` function

-    Interpret this value
